### 2025-06-12 manuscript.tex
affliation

	\begin{flushleft}
		\textbf{Viroon Kamchoom \textsuperscript{a}, Ankit Garg \textsuperscript{b}, Sai krishna Akash Ramineni \textsuperscript{c}, Thanu Harnpattanapanich \textsuperscript{d,e}, Phichet Ratanaprasatkul \textsuperscript{f}}
	\end{flushleft}

	\begin{flushleft}
		{\small {\textsuperscript{a}Excellent centre for green and sustainable infrastructure, Department of Civil Engineering, School of Engineering, King Mongkut's Institute of Technology Ladkrabang (KMITL), Bangkok, Thailand \\ 
				\textsuperscript{b}University in Shantou, Shantou, China \\ 
				\textsuperscript{c}Undergraduate, Department of Civil Engineering at IIT Indore, Indore city, Madhya Pradesh, Postal code- 453552, India \\
				\textsuperscript{d} Geotech Pillar co., ltd, Bangkok, Thailand \\
				\textsuperscript{e} Thailand Underground and Tunnelling Group, The Engineering Institute of Thailand, Thailand \\
				\textsuperscript{f} Bureau of Engineering and Architectural Design, Royal Irrigation Department (RID), Bangkok, Thailand \\
		}}
	\end{flushleft}

>>>>

	\begin{flushleft}
		\textbf{Sai krishna Akash Ramineni \textsuperscript{a}, Insha Wani \textsuperscript{b}, Ankit Garg \textsuperscript{c}, Viroon Kamchoom \textsuperscript{d}, Abdulla R. OMAROV \textsuperscript{e}}
	\end{flushleft}

	\begin{flushleft}
		{\small {\textsuperscript{a} Department of Civil Engineering at IIT Indore, Indore city, Madhya Pradesh, Postal code- 453552, India \\
				\textsuperscript{b} Former Research Scholar, IIT Jammu, India \\ 
				\textsuperscript{c} Department of Health and Environmental Sciences, Xi'an Jiaotong-Liverpool University, Suzhou, China \\
				\textsuperscript{d} Excellent centre for green and sustainable infrastructure, Department of Civil Engineering, School of Engineering, King Mongkut's Institute of Technology Ladkrabang (KMITL), Bangkok, Thailand \\
				\textsuperscript{e} Department of Construction Engineering, L.N Gumilyov Eurasian National University, Kazakhstan \\

		}}
	\end{flushleft}
